Dynamical modeling of tidal streams

### 2014-01-01 tex/ms.tex
streams: typo

Our calculation of the mean stream orbit as a function of angle along
the stream also points the way to determining the location of an
``orphan'' stream's progenitor (an orphan stream is a stream for which
the progenitor is not know). This requires high-quality data that
allows the average orbit as a function of position along the stream to
be determined. If this can be done, then the observation of a steady
change in the mean orbit followed by a plateau indicates that the
progenitor lies in the direction of the plateau. The change in the
mean orbit along the stream is a function of the mean orbit offset
($\Delta \Omega^m$ in the direction of $\Delta \opar$), the dispersion
in orbit offsets ($\sigma^2_{\Omega,1}$ in $\Delta \opar$), and the
disruption time $t_d$. The first two of these can be measured from the
width of the stream and the plateau in the mean orbit as a function of
stream position. The disruption time $t_d$ can then be measured from
the change in mean orbit at the end of the stream. With all of the
parameters of the forward model measured, we can extrapolate the
stream backward to the progenitor position. Similarly, we can
extrapolate a leading stream to its trailing counterpart, if this is
unknown (and vice versa).

>>>>

Our calculation of the mean stream orbit as a function of angle along
the stream also points the way to determining the location of an
``orphan'' stream's progenitor (an orphan stream is a stream for which
the progenitor is not know). This requires high-quality data that
allows the average orbit as a function of position along the stream to
be determined. If this can be done, then the observation of a steady
change in the mean orbit followed by a plateau indicates that the
progenitor lies in the direction of the plateau. The change in the
mean orbit along the stream is a function of the mean orbit offset
($\Delta \Omega^m$ in the direction of $\Delta \opar$), the dispersion
in orbit offsets ($\sigma_{\Omega,1}$ in $\Delta \opar$), and the
disruption time $t_d$. The first two of these can be measured from the
width of the stream and the plateau in the mean orbit as a function of
stream position. The disruption time $t_d$ can then be measured from
the change in mean orbit at the end of the stream. With all of the
parameters of the forward model measured, we can extrapolate the
stream backward to the progenitor position. Similarly, we can
extrapolate a leading stream to its trailing counterpart, if this is
unknown (and vice versa).
